Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-26 paper-ieee-trans.tex
answer to Pablo comment, fix some refs

The EC projects considered in this paper are listed chronologically in Table~\ref{tab:eup}.
Each project paved the way for the following ones, according to a logic evolution in which
the role of the quality and reliability of the software has
consistently increased. As shown in Table~\ref{tab:feat}, the most recent projects are more
committed to, and aware, of software reliability practices.
Table~\ref{tab:feat} also shows the topics addressed in the following sections, highlighting
the commonalities and specific features on software reliability.

@@

\bibitem{aiftimiei}
A. Aiftimiei, and D. Dongiovanni, et al.,
Improving the quality of EMI Releases by leveraging the
EMI Testing Infrastructure.
\emph{Journal of Physics: Conference Series},
vol. 396, 2012.

\bibitem{agile-manifesto}
Beck, K., Beedle, et al., (2001).
Manifesto for Agile Software Development.
[Online] Available: \url{http://www.agilemanifesto.org/}
[Accessed 4 Jun. 2018].

\bibitem{zhu}
L. Zhu and L. Bass and G. Champlin--Scharff,
DevOps and Its Practices,
\emph{IEEE Software},
vol. 33, n. 3, pp. 32--34, 2016.

\bibitem{soltesz}
S. Soltesz, and H. P\"{o}tzl, et. al.,
Container-based Operating System Virtualization: A Scalable, High-performance Alternative to Hypervisors,
\emph{SIGOPS Oper. Syst. Rev.},
vol. 41, n. 3, pp. 275--287, 2007.

\bibitem{radatz}
J. Radatz and A. Geraci and F. Katki.
IEEE Standard glossary of softare engineering terminology.
\emph{IEEE Std. 610.12-1990}, 1990.

\bibitem{sommerville}
I. Sommerville.
Integrated requiremetns envineering: A tutorial.
\emph{IEEE Software},
vol. 14, issue 1, pp. 16--23, 2005.

\bibitem{tashtoush}
Y. Tashtoush and Z. Odat, et al.
Impact of programming features on code readability.
\emph{International Journal of Software Engineering and its Applications}, 
vol. 7, issue 6, pp. 441--458, 2013.

\bibitem{buse}
R. P. Buse and W. R. Weimer.
Learning a metric for code readability.
\emph{IEEE Transactions on Software Engineering},
vol. 36, issue 4, pp. 546--558, 2010.

\bibitem{baggen}
R. Baggen and J. P. Correia, et al.
Standardized code quality benchmarking for improving software maintainability.
\emph{Software Quality Journal},
vol. 20, issue 2, pp. 287--307, 2012.

>>>>

The EC projects considered in this paper are listed chronologically in Table~\ref{tab:eup}.
Each project paved the way for the following ones, according to a logic evolution in which
the role of the quality and reliability of the software has
consistently increased. As shown in Table~\ref{tab:feat}, the most recent projects are more
committed to, and aware of, software reliability practices.
Table~\ref{tab:feat} also shows the topics addressed in the following sections, highlighting
the commonalities and specific features on software reliability.

@@

\bibitem{aiftimiei}
A. Aiftimiei, et al.,
Improving the quality of EMI Releases by leveraging the
EMI Testing Infrastructure.
\emph{J. Phys. Conf. Ser.},
vol. 396, 2012.

\bibitem{agile-manifesto}
K. Beck, et al., (2001),
Manifesto for Agile Software Development.
[Online] Available: \url{http://www.agilemanifesto.org/}
[Accessed 4 Jun. 2018].

\bibitem{zhu}
L. Zhu, L. Bass and G. Champlin--Scharff,
DevOps and Its Practices,
\emph{IEEE Softw.},
vol. 33, n. 3, pp. 32--34, 2016.

\bibitem{soltesz}
S. Soltesz, et. al.,
Container-based Operating System Virtualization: A Scalable, High-performance Alternative to Hypervisors,
\emph{SIGOPS Oper. Syst. Rev.},
vol. 41, n. 3, pp. 275--287, 2007.

\bibitem{radatz}
J. Radatz, A. Geraci and F. Katki,
IEEE Standard glossary of softare engineering terminology.
\emph{IEEE Std. 610.12--1990}, 1990.

\bibitem{sommerville}
I. Sommerville,
Integrated requirements engineering: A tutorial.
\emph{IEEE Softw.},
vol. 14, issue 1, pp. 16--23, 2005.

\bibitem{tashtoush}
Y. Tashtoush, et al.,
Impact of programming features on code readability.
\emph{Int. J. Softw. Eng. Appl.}, 
vol. 7, issue 6, pp. 441--458, 2013.

\bibitem{buse}
R. P. Buse and W. R. Weimer,
Learning a metric for code readability.
\emph{IEEE Trans. Softw. Eng.},
vol. 36, issue 4, pp. 546--558, 2010.

\bibitem{baggen}
R. Baggen, et al.,
Standardized code quality benchmarking for improving software maintainability.
\emph{Softw. Qual. J.},
vol. 20, issue 2, pp. 287--307, 2012.
